Report on Late Winter2013 Production: Image Differencing

### 2013-03-26 W13report.tex
Added summary of how many sigmas the image planes are different at detection.

@@

\item When deconvolving, the postfiltered variance is 70\% {\it
  higher} at the time of detection compared to the prefiltered data
  (Table~\ref{tab-variance2}).  This is consistent with the
  understanding that deconvolution increases high frequency noise in
  the images, and provides a {\it lower} detection efficiency in
  deconvolved data.  Prefiltering is clearly preferred in the case of
  significant deconvolution (v6866601; FWHM of 4.9 pixels matches to a
  FWHM of 3.5 pixels).

\item The postfilter pipeline can produce difference images with a
  minor deconvolution (v6866602; FWHM of 4.9 pixels matched to 4.9
  smoothed (v6866603; FWHM of 4.9 pixels matched to 6.7 pixels).

>>>>

For completeness, we note the median differences in the image plane at
the time of detection are 3--4 counts (or 0.2 sigma relative to the
empirical variance) for v6866601, 0.2 counts (sigma) for v6866602, and
less than 0.1 counts (sigma) for v6866603.

@@

\item When strongly deconvolving, the postfiltered variance is 70\%
  {\it higher} at the time of detection compared to the prefiltered
  data (Table~\ref{tab-variance2}).  This is consistent with the
  understanding that deconvolution increases high frequency noise in
  the images, and provides a {\it lower} detection efficiency in
  deconvolved data.  Prefiltering is clearly preferred in the case of
  significant deconvolution (v6866601; FWHM of 4.9 pixels matches to a
  FWHM of 3.5 pixels).

\item The postfilter pipeline can produce difference images with a
  minor deconvolution (v6866602; FWHM of 4.9 pixels matched to 4.9
  pixels) at a quality commensurate with a subtraction that uses a
  smoothing convolution (v6866603; FWHM of 4.9 pixels matched to 6.7
  pixels).
